KNNFinalYu

### 2021-05-13 DecisionTreeFinalYu.Rmd
Evaluation Metrics

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rio)
library(plyr)
library(tidyverse)
library(rpart)
library(psych)
library(pROC)
library(rpart.plot)
library(rattle)
library(caret)
library(C50)
library(mlbench)
install.packages("e1071")
library(e1071)
```

@@

```{r}
stroke <- read.csv("stroke.csv")

stroke$bmi <- gsub("N/A", NA, stroke$bmi)
stroke$smoking_status <- gsub("Unknown", NA, stroke$smoking_status)
stroke <- na.omit(stroke)

# Data Cleaning Specifically for Decision Tree

@@

# 0.4186047
```

@@

```{r}
tree_matrix <- confusionMatrix(as.factor(stroke_predict), as.factor(test_stroke$stroke), positive = "1", dnn = c("Prediction", "Actual"), mode = "sens_spec")

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rio)
library(plyr)
library(tidyverse)
library(rpart)
library(psych)
library(pROC)
library(rpart.plot)
library(rattle)
library(caret)
library(C50)
library(mlbench)
library(e1071)
```

@@

```{r}
stroke <- read.csv("stroke.csv")
stroke$bmi <- gsub("N/A", NA, stroke$bmi)
stroke$smoking_status <- gsub("Unknown", NA, stroke$smoking_status)
stroke <- na.omit(stroke)

# Data Cleaning Specifically for Decision Tree - Changing things to Binary

@@

# 0.2647059
```

@@

# Confusion Matrix 
```{r}
tree_matrix <- confusionMatrix(as.factor(stroke_predict), as.factor(test_stroke$stroke), positive = "1", dnn = c("Prediction", "Actual"), mode = "sens_spec")

@@

# ROC Curve
```{r}
Stroke_roc <- roc(as.numeric(test_stroke$stroke), as.numeric(stroke_predict), plot = TRUE)
Stroke_roc$auc
plot(Stroke_roc) 
```

### 2021-05-13 KNNFinalYu.Rmd
Evaluation Metrics

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DT)
library(caret)
library(class)
```

@@

```
# KNN Model with 3NN
```{r}
training_stroke
stroke_KNN <- knn(train = training_stroke[, -c(11)],
              test = test_stroke[, -c(11)],
              cl = training_stroke$stroke,
              k = 3,
              use.all = T,
              prob = T)

prb<- data.frame(prob = attr(stroke_KNN, "prob"))
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DT)
library(caret)
library(class)
library(ROCR)
library(MLmetrics)
```

@@

```
# KNN Model with 9NN
```{r}
training_stroke
stroke_KNN <- knn(train = training_stroke[, -c(11)],
              test = test_stroke[, -c(11)],
              cl = training_stroke$stroke,
              k = 3,
              use.all = T,
              prob = T)

prob_stroke<- data.frame(prob = attr(stroke_KNN, "prob"))
```

@@

# Evaluation Metrics
```{r}
prob_stroke <- prob_stroke %>%
  mutate(prob_stroke, target = as.numeric(stroke_KNN))
prob_stroke$target <- as.numeric(recode(prob_stroke$target, '2' = '1', '1' = '0'))

prob_stroke <- prob_stroke %>%
  mutate('1' = ifelse(prob_stroke$target =='1', prob_stroke$prob, 1-prob_stroke$prob))

prob_stroke <- prob_stroke%>%
  mutate('0' = 1-prob_stroke$`1`)

LogLoss(as.numeric(prob_stroke$`1`), as.numeric(test_stroke$stroke)) # 2.820455
F1_Score(as.numeric(stroke_KNN), as.numeric(test_stroke$stroke)) # 0.2739726

# ROC/AUC Output
```{r}
stroke_eval <- data.frame(pred_class = stroke_KNN, pred_prob = prob_stroke$`1`, target = as.numeric(test_stroke$stroke))
pred_stroke <- prediction(stroke_eval$pred_prob, stroke_eval$target)

stroke_perf <- performance(pred_stroke, "tpr","fpr")
plot(stroke_perf, colorize = TRUE) + abline(a=0,b=1)
stroke_perf_AUC <- performance(pred_stroke, "auc")
print(stroke_perf_AUC@y.values) # AUC 0.7771214
